Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-04-10 2017-Xudong-SMT/OpenPNets-SMT.tex
Add the example for Presentation
Examples are added in page 13, and corresponding modification in page 20.

First example we choose is a formula $a.P||b.Q$, composing prefix and
parallel operators of value-passing CCS, and containing two process
variables (holes) P and Q. In Fig. 1, we show the encoding of this CCS
formula. The pNet has a tree-like structure.

@@

An algebra presentation contains:
\begin{itemize}
	\item Sorts: Constants sets of the algebra, types of the data
          and actions. 
	\item Operators: Operators used to construct action
          expressions (including their data parameters); they are
          constructors of data and action sorts, but also predicates
          over these objects.
        \item Constants: The satifiability solver need to know which
          actions in the pLTS behaviours are constants (like the $l$,
          $r$ local actions of the controlers in the CCS example). So
          for a given pNet system, the Action sort will include all
          these constants.
\end{itemize}

@@

\paragraph{Operators}
We need introduce operators for building expressions, of both action
and data sorts, when encoding the 
algebra into pNets. So that is needed to know about the input and
output of the operators used in the expressions from those
algebra. The input and output should belong to the sorts on the
pNet. When there are $k$ subnets in this pNet, the structure of a
$n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.

@@

@@

The $datatypes$ are declared according to the $sorts$ the users declared in the $presentation$. If the return type of the $functions$ is one of the $datatypes$, we add this $function$ when declare the $datatypes$, it present the reality that every action expression also belongs to a sort of pNet. Although in Fig~\ref{schema:smt-lib} we have not declared $functions$, they should be exactly declared if there are new $operators$ declared in the $presentation$. The input type of the $function$ can be $Int$, $Bool$ or the $datatypes$ declared all determined by the construct of the  $operators$ in the presentation. For example, we define a new operator to present the equation between two actions in CCS example $\text{EQUAL}$ in the format likes:

>>>>

First example we choose is a formula $a.P||b.Q$, composing prefix and
parallel operators of value-passing CCS, and containing two process
variables (holes) P and Q. In Fig.~\ref{schema:ccs-pnets}, we show the encoding of this CCS
formula. The pNet has a tree-like structure.

@@

An algebra presentation contains:
\begin{itemize}
	\item Sorts: Constants sets of the algebra, types of the data
          and actions. 
	\item Operators: Operators used to construct action
          expressions (including their data parameters); they are
          constructors of data and action sorts, but also predicates
          over these objects.
        \item Constants: The satisfiability solver need to know which
          actions in the pLTS behaviors are constants (like the $l$,
          $r$ local actions of the controllers in the CCS example). So
          for a given pNet system, the Action sort will include all
          these constants.
\end{itemize}

@@

\QIN{
In the CCS example, we have a sort for actions called $Action$:
}

\[ Action = \{ l, r\} \]

\paragraph{Operators}
We need introduce operators for building expressions, of both action
and data sorts, when encoding the 
algebra into pNets. So that is needed to know about the input and
output of the operators used in the expressions from those
algebra. The input and output should belong to the sorts of the
pNet. When there are $k$ sorts in this pNet, the structure of a
$n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.

\QIN{For instance, in our CCS running example, there is the action expression $!ch(v)$ using an operator $!$ presenting the ``$EMIT$'' action in CCS. We only use a sort called $Action$ to involve all the constant actions or action expressions in pNets and other parameters such as channel $ch$ or variable $v$ are all integers. So here we treat $EMIT$ as a binary operator with the format like:
}

 \[ < Int, Int > \rightarrow Action . \]

@@

\QIN{The translation of the presentation in the Z3 SMT solver will be given later.
}

@@

The $datatypes$ are declared according to the $sorts$ the users declared in the $presentation$. If the return type of the $functions$ is one of the $datatypes$, we add this $function$ when declare the $datatypes$, it present the reality that every action expression also belongs to a sort of pNet.

\QIN{
So when we declare the operator EMIT we illustrated in section 4.1, it will be just declared together with the constants.
}

 Although in Fig~\ref{schema:smt-lib} we have not declared $functions$, they should be exactly declared if there are new $operators$ declared in the $presentation$. The input type of the $function$ can be $Int$, $Bool$ or the $datatypes$ declared all determined by the construct of the  $operators$ in the presentation. For example, we define a new operator to present the equation between two actions in CCS example $\text{EQUAL}$ in the format likes:
